An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex

To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links} on the right:
\begin{equation}\label{eq:abstain-link}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
In particular, Theorem~\ref{thm:eps-thick-calibrated} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
It would be interesting to compare the two links in practice.

\begin{figure}
\begin{center}
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
\end{minipage}\hfill
\caption{Left: Possible optimal reports given by our $\psi$ constructed using $\|\cdot\|_\infty$ and $\epsilon = 1/2$.  Middle: Two examples of $U \in \U$ and their thickened regions for $\|\cdot\|_1$ and $\epsilon = 1$. Right: Link values given by our $\psi$ constructed using $\|\cdot\|_1$ and $\epsilon = 1$}
\label{fig:abstain-links}
\end{center}
\end{figure}

>>>>

To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links} on the right:
\begin{equation}\label{eq:abstain-link-1}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
In particular, Theorem~\ref{thm:eps-thick-calibrated} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
It would be interesting to compare the two links in practice.

\begin{figure}
\begin{center}
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
\end{minipage}\hfill
\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$. The embedding is shown in bold labeled by the corresponding reports. (L) The map $\Psi$ resulting from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.  (M) An illustration of the thickened sets from Definition~\ref{def:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$. (R) The $\Psi$ and $\psi$ from Theorem~\ref{thm:eps-thick-calibrated} using $\|\cdot\|_1$ and $\epsilon = 1$}
\label{fig:abstain-links}
\end{center}
\end{figure}
